$P$ versus $NP$

### 2019-11-22 doc/presentation.tex
Updated the presentation doc

Sauerhoff has shown the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).

>>>>

Sauerhoff has investigated the class $BNL$ of languages recognizable by nondeterministic logarithmic space Turing machine, that only use nondeterministic moves before reading their input ($``$nondeterminism at the beginning$"$).
